---
title: "Proficiency Test 2"
author: 
  name: Caitlin A. Kane
format: html
editor: visual
---

## Task - 1

```{r}
for(i in 1:length(mtcars)){
  print(mtcars$mpg[1:3])
}
```
\newpage
## Task - 2
```{r}
count_above <- function(data,count,cutoff){ #assigns the function
  count_above
  
  for (i in 1:length(count)){ #defines what the function is doing 
    if(count[i] > cutoff){
      count<- count+1 #for instance, the function with take the count and add 1 to it 
    }
  }
  return(count) #This is what the code will give you when ran 
}
```
How many flowers have a seapl length greater than 6 cm in the iris dataset?
```{r}

count_above(iris, iris$Sepal.Length, 6)

```
How many cars have a value greater than or equal to 150 disp in the mtcars dataset?
```{r}

count_above(mtcars, mtcars$disp, 150)
```
\newpage

## Task - 3

The concept of masking functions involves when a new package hides a function from an older package. For example, you install a package in R and it hides a function from an already installed package on your R. 

\newpage 

## Task - 4

```{r}
iris$Sepal.Length[1]
iris[1,1]
```
The first code returns the first value of the iris data set for Sepal.Length. 

The iris[1,1] returns the value for the first row, first column data point, which in this case is the first vale of the Sepal.Length column for the iris data set. Therefore, they produce the same output. 
